Flowchart of Current Algorithm

### 2009-01-20 docs/flowchart/flowchart.tex
added a mini flow chart of variable names at the end of this section

\section{Outstanding Questions}

\begin{enumerate}

\item Why do we only update the temperature at the end of steps 4 and
      8.  This means that at the top of the algorithm, the temperature
      going into {\bf React State} in step 2 does not include the
      effects of the previous reactions.

      To be thermodynamically consistent, I think that we need to
      update the temperature at the very end of step 9.  That way we
      end the time-level update with $T^{n+1}$ instead of $T^{(2)}$,
      and we go into the next sequence, step 2 with a valid temperature.

\item Why is there no equivalent of $\etarho$ for enthalpy---e.g.\ an
      $\eta_{\rho h}$?

>>>>

In summary:
\begin{equation}
\left.\begin{array}{ccccccccc}
& \text{React State} & & \text{Advect State} & & \text{Diffuse Enthalpy} & & \text{React State} & \\
\rho^n & & & \longrightarrow & & & & & \rho^{n+1} \\
(\rho X)^n & \longrightarrow & (\rho X)^{(1)} & \longrightarrow & & & (\rho X)^{(2)} & \longrightarrow & (\rho X)^{n+1} \\
(\rho h)^n & \longrightarrow & (\rho h)^{(1)} & \longrightarrow & (\rho h)^{(2a)} & \longrightarrow & (\rho h)^{(2)} & \longrightarrow & (\rho h)^{n+1}\\
T^n & \longrightarrow & T^{(1)} & & & \longrightarrow & T^{(2)} & \longrightarrow & T^{n+1} \\
\end{array}\right.\nonumber
\end{equation}
\begin{equation}
\left.\begin{array}{ccccccccc}
& \text{React Base} & & \text{Advect Base} & & \text{Correct Base} & & \text{React Base} & \\
\rho_0^n & & & \longrightarrow & \rho_0^{(2a)} & \longrightarrow & & & \rho_0^{n+1} \\
(\rho h)_0^n & \longrightarrow & (\rho h)_0^{(1)} & \longrightarrow & & & (\rho h)_0^{(2)} & \longrightarrow & (\rho h)_0^{n+1} \\
p_0^n & & & \longrightarrow & & & & & p_0^{n+1} \\
\end{array}\right.
\end{equation}
Note that this chart indicates, for example, that $\rho^n = \rho^{(1)}$, $\rho^{(2a)} = \rho^{(2)} = \rho^{n+1}$, etc.
